%\begin{acknowledgement}
Here, I would like to sincerely acknowledge individuals who have supported me directly or indirectly for the accomplishment of this paper.

First of all, I would like to express my sincere gratitude to my first supervisor Prof. Dr. Xiaoming Fu for his helpful suggestions for me and for my paper. Secondly, I would like to thank Dr. Tingting Yuan for being my second supervisor and guiding me with her comments.  Next,  I would like  to specially thank Mr. Yachao Shao, who has been my advisor throughout the journey towards completion of my paper. I would like to thank him for his constant encouragement, guidance and tireless assistance. Without their usual and enlightening guidance, this paper would not have been in its present form.

I would like to thank my dear family for their love and great faith in me for many years, even though they cannot be beside me. I also want to thank my dear friends and my roommate, who have given me help and time to listen to my opinions and comforted me when I felt upset or faced difficulties. While it would be difficult to list all their names, I would like to express my gratitude to each of my family members and friends in China and in Germany. Without their support and help, the completion of this paper would not have been possible.

Finally, I would like to thank the faculty of Computer Science of the Georg-August University of G{\"o}ttingen. I would like to thank all the staff members of the department who have provided me with information required and answered my questions with patience.

%\end{acknowledgement}
